Cleaning our own Dust: Simulating and Separating Galactic Dust Foregrounds with Convolutional Networks

### 2018-08-10 PAPER/main.tex
minor changes to section 2

A Generative Adversarial Network (GAN) is a form of unsupervised machine learning which attempts to model a generating function which can create samples from a desired distribution \citep{goodfellow14}. 
A GAN consists of two sub-models, a discriminator and a generator, each with their own sets of weights that are to be optimized.
The discriminator is optimized to detect samples from $P$, the distribution which we desire to emulate, and the generator is optimized to create samples from $P$.
During the training process the discriminator is shown labeled samples from $P$ and from the generator, as the discriminator improves at detecting samples from $P$ the generator must improve at creating samples belonging to $P$ to minimize its own loss function. Training proceeds until the generator's output distribution has converged to $P$.
For the case of generating $N\times M$ pixel images a Deep Convolutional GAN (DCGAN), first presented in \cite{radford15}, has proven to be effective. In this architecture the generator $\rm{G}(z)$ maps $z$, a random vector from $Z$, to $P$ in $\mathbb{R}^{N\times M}$ through a series of upsamplings via convolutions. 
The generator then allows one to perform importance sampling as $Z$ is a distribution where it is known how to produce samples i.e. a Gaussian distribution.

In our case $P$ is the thermal distribution of interstellar dust across the sky.
A DCGAN allows us to generate simulations of dust intensity maps based on the actual measured distribution instead of relying on a particular set of assumptions. 
As we only have one sky to measure we are limited in our ability to measure samples from $P$ and instead focus on a subset of $P$, patches of sky with approximately 1\% coverage. 
The primary reason for choosing 1\% versus some other size is this coverage reduces the computational power needed to develop a model while still covering angular scales of interest.

@@

$\it{move this}$
Generally validation of a neural network's predictions or outputs is done against a subset of the training data to test if a model has overfit the data or generalized well. However we do not follow this practice for two reasons. First, we only have roughly 1000 images in our dataset, splitting this into a training and validation set would result in too few samples for either set. Second, the process of mapping portions of the sky to a Cartesian plane without overlap would leave portions of the full sky unsampled and significantly reduce the size of our dataset. We therefore rely on maps with some overlap. Even if we split this set into a training and validation set a significant amount of correlation would remain due to the overlap of the individual maps. We are then left with the task of showing the generated samples are not simply one-to-one copies of the input set. $\it{need to think about tests for this}$

@@

>>>>

A Generative Adversarial Network (GAN) is a form of unsupervised machine learning which attempts to model a generating function which can create samples from a desired distribution \citep{goodfellow14}. 
A GAN consists of two sub-models, a discriminator and a generator, each with their own sets of weights that are to be optimized.
The discriminator is optimized to detect samples from $P$, the distribution which we desire to emulate, and the generator is optimized to create samples from $P$.
During the training process the discriminator is shown labeled samples from $P$ and from the generator, as the discriminator improves at detecting samples from $P$ the generator must improve at creating samples belonging to $P$ to minimize its own loss function. Training proceeds until the generator's output distribution has converged to $P$.
For the case of generating $N\times M$ pixel images a Deep Convolutional GAN (DCGAN), first presented in \cite{radford15}, has proven to be effective. In this architecture the generator $\rm{G}(z)$ maps $z$, a random vector from $Z$, to $P$ in $\mathbb{R}^{N\times M}$ through a series of upsamplings via convolutions. 
The generator then allows one to sample from $P$ as $Z$ is a distribution where it is known how to produce samples i.e. a Gaussian distribution.

In our case $P$ is the thermal distribution of interstellar dust across the sky.
A DCGAN allows us to generate simulations of dust intensity maps based on the actual measured distribution instead of relying on a particular set of assu
mptions. 
As we only have one sky to measure we are limited in our ability to measure samples from $P$ and instead focus on a subset of $P$, patches of sky with approximately 1\% coverage. 
The primary reason for choosing 1\% versus some other size is this coverage reduces the computational power needed to develop a model while still covering angular scales of interest.

@@

@@

Generally validation of a neural network's predictions or outputs is done against a subset of the training data to test if a model has overfit the data or generalized well. However we do not follow this practice for three reasons. First, we only have roughly 1000 images in our dataset, splitting this into a training and validation set would result in too few samples for either set. Second, the process of mapping portions of the sky to a Cartesian plane without overlap would leave portions of the full sky unsampled and significantly reduce the size of our dataset. We therefore rely on maps with some overlap. Even if we split this set into a training and validation set a significant amount of correlation would remain due to the overlap of the individual maps. Finally, since we are not working with a classification problem we are not concerned about generalizing, we are trying to produce samples from a specific distribution. For a large enough data set the summary statistics for testing and validation sets would be the same, as they are drawn from the same distribution, and fitting the testing set well would automatically imply the validation set is also well fit. We are then left with the task of showing the generated samples are not simply one-to-one copies of the input set. This can be done by exploring the latent space for any hard transitions. We do this via the power spectra and find that drawing many samples does sufficiently fill the one sigma region.
